---
title: "Homework 3"
author: "Jade Butler"
date: "`r Sys.Date()`"
output: openintro::lab_report
---

```{r load-packages}
library(tidyverse)
library(openintro)
library (ggpubr)
library(car)
```

### Problem 1
#### Part a
```{r Read in data and make histograms}
Pdat <- read.csv("PlasmaRetinolData.csv")
h1 <- ggplot(data = Pdat, aes(x = BetaDiet)) +
  geom_histogram(bins = 6, colour = 1, fill = "white") + xlab("Dietary beta-carotene consumed")
h2 <- ggplot(data = Pdat, aes(x = BetaPlasma)) +
  geom_histogram(bins = 6, colour = 1, fill = "white") + xlab("Plasma beta-carotene (ng/ml)")
h3 <- ggplot(data = Pdat, aes(x = log(BetaDiet))) +
  geom_histogram(bins = 6, colour = 1, fill = "white") + xlab("Dietary beta-carotene consumed [natural log]")
h4 <- ggplot(data = Pdat, aes(x = log(BetaPlasma))) +
  geom_histogram(bins = 6, colour = 1, fill = "white") + xlab("Plasma beta-carotene (ng/ml) [natural log]")
ggarrange(h1, h2, h3, h4 + rremove("x.text"),
          ncol = 2, nrow = 2)
```

#### Part b
```{r count zeros}
Pdat <- read.csv("PlasmaRetinolData.csv")
Pdat %>% filter(BetaDiet == 0 | BetaPlasma == 0) # The vertical bar is "OR"; use & for "AND"
```
Only one observation is impacted by the natural log observation.

#### Part c
```{r no zeros}
Pdat <- read.csv("PlasmaRetinolData.csv")
Pdat2 <- Pdat %>% filter(BetaDiet>0 & BetaPlasma>0)
```

### Problem 2

#### Part a)
```{r scatterplot}
ggplot(Pdat2, aes(x=Pdat2$BetaDiet, y=Pdat2$BetaPlasma)) +
             geom_point() +  geom_smooth(method = "lm", se = FALSE) +
             xlab("Dietary Beta-carotene (mcg/day)") + 
             ylab("Plasma Beta-carotene (ng/ml)")
cor(Pdat2$BetaDiet, Pdat2$BetaPlasma)
```
 
The correlation between Dietary Beta-carotene and Plasma Beta-carotene is positive given by the R-value of 0.22, but is only a moderate positive correlation.

#### Part b)

```{r scatterplot2}
ggplot(Pdat2, aes(x=BetaDiet, y=log(BetaPlasma))) + 
  geom_point(size=1, shape=19) + xlab("Dietary Beta-Carotene (mcg/day") +
  ylab("Natural Log Plasma Beta-carotene (ng/ml)")
cor(Pdat2$BetaDiet, log(Pdat2$BetaPlasma))
```
 An r coefficent of 0.19 indicates a positive but fairly weak correlation.
 
#### Part c)

```{r scatterplot3}
ggplot(Pdat2, aes(x=log(BetaDiet), y=BetaPlasma)) + 
  geom_point(size=1, shape=19) + xlab(" Natural Log Dietary Beta-Carotene (mcg/day") +
  ylab("Plasma Beta-carotene (ng/ml)")
cor(log(Pdat2$BetaDiet),Pdat2$BetaPlasma)
```
With an r coefficient value of 0.203 we have a moderate positive correlation which is well demonstrated on the scatter plot.

#### Part d)

```{r scatterplot4}
ggplot(Pdat2, aes(x=log(BetaDiet), y=log(BetaPlasma))) + 
  geom_point(size=1, shape=19) + xlab(" Natural Log Dietary Beta-Carotene (mcg/day") +
  ylab("Natural Log Plasma Beta-carotene (ng/ml)")
cor(log(Pdat2$BetaDiet),log(Pdat2$BetaPlasma))
```
With a r coefficient of 0.187, we still have a positive correlation in this natural log data set but it is a weak positive correlation.

#### Part e)
Based on this modeling I would recommend a natural log on the dietary beta-carotene and no natural log on the plasma beta-carotene as this left us with the strongest r coefficent or correlation value among the data sets which will better meet assumptions.

### Problem 3
```{r scatterplot4a}
ggplot(Pdat2, aes(x=log(BetaDiet), y=log(BetaPlasma))) + 
  geom_point(size=1, shape=19) +  geom_smooth(method = "lm", se = FALSE) + xlab(" Natural Log Dietary Beta-Carotene (mcg/day") +
  ylab("Natural Log Plasma Beta-carotene (ng/ml)")
lm.out <- lm(formula = Pdat2$BetaDiet ~ Pdat2$BetaPlasma)
summary(lm.out)
```
$\hat{y}$=1.7956x+1847.238

### Problem 4

With an estimated slope of 1.796, for every one unit of dietary beta-carotene, there is 1.796 units of plasma beta-carotene.

### Problem 5
```{r calculations1}
lnBetaPlasma = 1847.238 +  1.7956 * log(2100)
B <- log(1860.974)


### Problem 6

exp(B)
```
### Problem 7

Beta Plasma would be at about 200 on the original BetaDiet v. BetaPlasma plot and regression line.

### Problem 8

With a mild correlation Beta Diet can be used to estimate Beta Plasma but it may not be accurate enough as it does not have a very strong correlation where at it's max it is a 0.2. With an r^2 value of 4%, only 4% of the variability can be explained by Beta Diet.
