---
title: "Homework 6"
author: "Jade Butler"
date: "`r Sys.Date()`"
output: openintro::lab_report
---

```{r load-packages, message=FALSE}
library(tidyverse)
library(openintro)
library(rmarkdown)
library(BSDA) # you must install this first
```

### Problem 1
#### Part A
``` {r count and find means}
ICE <- read_csv("IceCream.csv")
#alpha = 0.1 df=200-1=199
ICE %>% glimpse
ICE %>% count(Puzzle)
mean(ICE$Puzzle) 
sd(ICE$Puzzle)
qt(0.05,199)
tsum.test(mean(ICE$Puzzle), sd(ICE$Puzzle), 200, conf.level = 0.90)$conf.int
t.test(ICE$Puzzle, conf.level = 0.90)

```
Interpretation: we are 90 percent confident that the mean puzzle scores of high school students fall between 51.15 points and 53.65 points.


#### Part B

```{r difference in mean puzzle scores}
Male <- ICE %>% filter(Sex == "0")
Female <- ICE %>% filter(Sex == "1")
SDM <- sd(Male$Puzzle) - sd(Female$Puzzle)
SDM
DFM <- mean(Male$Puzzle) - mean(Female$Puzzle)
DFM
tsum.test(DFM, SDM, 200, conf.level = 0.90)$conf.int
t.test(Male$Puzzle, Female$Puzzle, conf.level = 0.9)
```

Interpetation: we are 90% confident the difference in means of puzzle scores between male and female high school students is about -0.997 and -1.126 points.

### Problem 2
#### Part A
van-choc
Sig level = 10%
CI = 90
```{r subsets and SDs}
CHOC <- ICE %>% filter(Flavor == "2") 
CHS <- sd(CHOC$Video)
CHS
VAN <- ICE %>% filter(Flavor == "1")
VHS <- sd(VAN$Video)
VHS
```
#### Part B
```{r comparing means}
SDI <- VHS - CHS
SDI
MI <- mean(VAN$Video) - mean(CHOC$Video)
MI
tsum.test(MI, SDI, 200, conf.level = 0.90)$conf.int
### not sure how to execute t.test, excuted both tsum.test and t.test
t.test(VAN$Video, CHOC$Video, conf.level = 0.9)
```
With these values we can infer that the difference in mean Video Game scores between chocolate and vanilla favorite ice cream flavors will fall between 3.82 and 4.17 with 90% confidence.

#### Part C

In comparing both video game score means for vanilla and chocolate ice cream flavors, we can tell that on average those who prefer chocolate will most likely have a greater video game score denoted by the negative difference between video games scores when we subtract the vanilla mean from the chocolate mean.


### Problem 3
SI = 1 CI = 99 df= 21
```{r CI Smokers}
BW <- read_csv("Birthweight.csv")
SMOKER <- BW %>% filter(Smoker == "1")
NONSMOKER <- BW %>% filter(Smoker == "0")
count(SMOKER)
count(NONSMOKER)
mean(BW$Smoker)
sd(BW$Smoker)
t.test(BW$Smoker, conf.level = 0.99)
```
With this data we have 99% confidence that the mean proportion of participants who's mothers were smokers will fall between 0.313 and 0.734 which is accurate with the true mean of the proportion of population falling at 52%.

### Problem 4
#### Part A

```{r low birthweight}
#SL = 0.01 df = 42-1=41 p-value = 1.682878
count(BW)
Q <- qt(0.05,41)
Q
mean(SMOKER$LowBWt)
mean(NONSMOKER$LowBWt)
sd(SMOKER$LowBWt)
sd(NONSMOKER$LowBWt)
```
``` {r test}
#Smoker CI
SE = 0.42 / sqrt(42)
SE
C1 = mean(SMOKER$LowBWt) - qt(0.05,1) * (SE)
C2 = mean(SMOKER$LowBWt) + qt(0.05,1) * (SE)
C1 
C2
# We can see here that 11.820% to 33.63% of babies who's mothers were smokers are born with a low birthweight.

#non smoker CI
C3 = mean(NONSMOKER$LowBWt) - qt(0.05,1) * (SE)
C4 = mean(NONSMOKER$LowBWt) + qt(0.05,1) * (SE)
C3
C4

# We can also see that the proportion of babies with a low birthweight who's mothers were non-smokers lies between 5% to 15%

```
#### Part B
```{r proptest birthweight}
count(SMOKER %>% filter(LowBWt == "1"))
count(SMOKER)
#5 smokers had low birthweight out of 22 smokers

count(NONSMOKER %>% filter(LowBWt == "1"))
count(NONSMOKER) 
# 1 nonsmokers had a low birthweight out of 20 nonsmokers

prop.test(x = c(5, 1), n = c(22, 20))

count(LowBWt)

```
#### Part C

I beleive the sample size is large enough as it is <40 and the hypothesis that the proportion of low birthweight babies is higher for mothers that smoked is indeed true.

### Problem 5
#### Part A
```{r Cholesterol}
#oat bran - cornflake 
# 5% SI, 95% CI
CHOL <- read_csv("Cholesterol.csv")
Corn <- CHOL %>% filter(Cereal == "Cornflk")
mean(Corn$Cholesterol) #5.645
sd(Corn$Cholesterol) #0.788
Oat <- CHOL %>% filter(Cereal == "OatBran")
mean(Oat$Cholesterol) #5.3
sd(Oat$Cholesterol) #0.8838552

```
#### Part B


### Problem 6
#### Part A



#### Part B







