---
title: "Homework 6"
author: "Jade Butler"
date: "`r Sys.Date()`"
output: openintro::lab_report
---

```{r load-packages, message=FALSE}
library(tidyverse)
library(openintro)
library(rmarkdown)
library(BSDA) # you must install this first
```

### Problem 1
#### Part A
``` {r count and find means}
ICE <- read_csv("IceCream.csv")
#alpha = 0.1 df=200-1=199
ICE %>% glimpse
ICE %>% count(Puzzle)
mean(ICE$Puzzle) 
sd(ICE$Puzzle)
qt(0.05,199)
tsum.test(mean(ICE$Puzzle), sd(ICE$Puzzle), 200, conf.level = 0.90)$conf.int

```
Interpretation: we are 90 percent confident that the mean puzzle scores of high school students fall between 51.15 points and 53.65 points.


#### Part B

```{r difference in mean puzzle scores}
Male <- ICE %>% filter(Sex == "0")
Female <- ICE %>% filter(Sex == "1")
SDM <- sd(Male$Puzzle) - sd(Female$Puzzle)
SDM
DFM <- mean(Male$Puzzle) - mean(Female$Puzzle)
DFM
tsum.test(DFM, SDM, 200, conf.level = 0.90)$conf.int
```
Interpetation: we are 90% confident the difference in means of puzzle scores between male and female high school students is about -0.997 and -1.126 points.

### Problem 2
#### Part A
van-choc
Sig level = 10%
CI = 90
```{r subsets and SDs}
CHOC <- ICE %>% filter(Flavor == "2") 
CHS <- sd(CHOC$Video)
CHS
VAN <- ICE %>% filter(Flavor == "1")
VHS <- sd(VAN$Video)
VHS
```
#### Part B
```{r comparing means}
SDI <- VHS - CHS
SDI
MI <- mean(VAN$Video) - mean(CHOC$Video)
MI
tsum.test(MI, SDI, 200, conf.level = 0.90)$conf.int
```
With these values we can infer that the difference in mean Video Game scores between chocolate and vanilla favorite ice cream flavors will fall between 3.82 and 4.17 with 90% confidence.
#### Part C

In comparing both video game score means for vanilla and chocolate ice cream flavors, we can tell that on average those who prefer chocolate will most likely have a greater video game score denoted by the negative difference between video games scores when we subtract the vanilla mean from the chocolate mean.


### Problem 3



### Problem 4
#### Part A



#### Part B



#### Part C



### Problem 5
#### Part A



#### Part B


### Problem 6
#### Part A



#### Part B







