---
title: "Lesson 2, Lectures 2 and 3"
author: "Tamre Cardoso"
date: "`r Sys.Date()`"
output: openintro::lab_report
---
  
```{r load-packages, message=FALSE}
library(tidyverse)
library(openintro)
```

#### Read in data
```{r read in patient data}
PDat <- read_csv("Patient_Data.csv")
# Create a factor variable for Sex; the levels will be in alphabetical order
PDat$Sex <- factor(PDat$Sex)
```

#### Dot Plot
```{r dotplot}
p1 <- ggplot(data = PDat, aes(x = SystolicP)) +
         geom_dotplot(dotsize = 0.4, method="histodot", binwidth=2)
# Create p1 with proper x-axis label
p1 <- ggplot(data = PDat, aes(x = SystolicP)) +
         geom_dotplot(dotsize = 0.4, method="histodot", binwidth=2) + xlab("Systolic Pressure (mm Hg)")
# Add theme to remove y-axis labeling
p1 + theme(axis.text.y=element_blank(),axis.ticks.y=element_blank(),axis.title.y=element_blank())
```

#### Stem and Leaf Plot
```{r stem and leaf}
stem(PDat$SystolicP)
```

#### Histograms
```{r histogram}
# ggplot default
ggplot(data = PDat, aes(x = Weight)) +
  geom_histogram()
# ggplot binwidth = 10
ggplot(data = PDat, aes(x = Weight)) +
  geom_histogram(binwidth = 10)
# ggplot bins = 10; add proper axis label; add density curve
ggplot(data = PDat, aes(x = Weight)) +
  geom_histogram(aes(y = ..density..), bins = 10,
                 colour = 1, fill = "white") + 
  xlab("Patient Weight (lbs)") + geom_density()
# group by a categorical variable
ggplot(data = PDat, aes(x = Weight, fill = Sex, colour=Sex)) +
  geom_histogram(bins = 10, alpha = 0.5, position="identity") + 
  xlab("Patient Weight (lbs)")
```

#### Filtering Data
```{r filtering data}
# We can filter a data set to select subsets of data
# Instead of plotting all the weight data together
# we can create subset for males and females

# piped filter
PDat %>%
  filter(Sex == "F") %>%
  ggplot(aes(x = Weight)) +
  geom_histogram(bins = 10, colour = 1, fill = "white") + 
  xlab("Patient Weight Females (lbs)")
PDat %>%
  filter(Sex == "M") %>%
  ggplot(aes(x = Weight)) +
  geom_histogram(bins = 10, colour = 1, fill = "white") + 
  xlab("Patient Weight Males (lbs)")

# Use a facet wrap instead
ggplot(data = PDat, aes(x = Weight)) +
  geom_histogram(bins = 10, colour = 1, fill = "white") + 
  xlab("Patient Weight (lbs)") + facet_wrap(vars(Sex))

# Saving subsets to use for other calls later
# PDat.F and PDat.M can be used in other code
PDat.F <- filter(PDat, Sex == "F")
PDat.M <- filter(PDat, Sex == "M")
```

#### Univariate summary statistics for numeric variables

The summary and sd functions quickly provide basic summaries. The full line of code is included in ( ) so that the output of wt.summary and wt.sd are printed. A different function, summarize( ) may be used to customize the summary statistics that you want into one output. See Chapter 3 of Statistical Inference for Data Science for many examples. 

```{r Summary stats}
# You may need to include the argument na.rm=TRUE to remove
# observations with missing values
(wt.summary <- summary(PDat$Weight)) # gives a six number sample summaries
(wt.sd <- sd(PDat$Weight)) # gives sample standard deviation

# Use summarize function
# You can add the metrics your want
# This code shoes min, mean, Q1, Median, Q3, Max and SD
(sum.weight <- PDat %>% summarize(mean = mean(Weight, na.rm=TRUE),
                                 SD = sd(Weight, na.rm=TRUE)))
(sum.weight <- PDat %>% summarize(Min = min(Weight, na.rm=TRUE), 
                                  Q1 = quantile(Weight, 0.25, na.rm=TRUE),
                                  Median = quantile(Weight, 0.50,
                                                    na.rm=TRUE),
                                  Q3 = quantile(Weight, 0.75, na.rm=TRUE),
                                  Max = max(Weight, na.rm=TRUE),
                                  mean = mean(Weight, na.rm=TRUE),
                                  SD = sd(Weight, na.rm=TRUE)))
```

#### Boxplots
```{r ggplot2 boxplots}
p <- ggplot(PDat, aes(x=Weight, y="")) +
        geom_boxplot() + 
        xlab("Patient Weight (lbs)") +
        ylab("")
p
# Rotate the box plot
p + coord_flip()
# Notched box plot
p <- ggplot(PDat, aes(x=Weight, y="")) +
        geom_boxplot(notch=TRUE) + 
        xlab("Patient Weight (lbs)") +
        ylab("")
p
```

#### Comparative boxplots
```{r ggplot2 comparative boxplot}
# Using ggplot2
p <- ggplot(PDat, aes(x=Sex, y=Weight)) + 
  geom_boxplot() + xlab("Sex") +
  ylab("Patient Weight (lbs)")
p
# Rotate the box plot
p + coord_flip()
# Notched box plot
ggplot(PDat, aes(x=Sex, y=Weight)) + 
  geom_boxplot(notch=TRUE) + xlab("Sex") +
  ylab("Patient Weight (lbs)")
# Change outlier, color, shape and size
ggplot(PDat, aes(x=Sex, y=Weight)) + 
  geom_boxplot(outlier.colour="red", outlier.shape=8,
                outlier.size=4) + xlab("Sex") +
  ylab("Patient Weight (lbs)")
```       